Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-03 02_Paper/paper.tex
Fixing corresponding author
intro

\author[a]{Peter Burggräf}
\author[a]{Johannes Wagner}
\author[a]{Benjamin Koke}
\author[a]{Fabian Steinberg} 
\author[a]{Alejandro R. Pérez M.}
\author[a]{Lennart Schmallenbach}
\author[b,c]{Jochen Garcke}
\author[b]{Daniela Steffes-lai}
\author[b,d]{Moritz Wolter}

@@

\begin{itemize}
       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
       \item \textbf{Conclusion}, express the remarks and diskoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
\end{itemize}

@@

Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle. For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and diskarded if so. At this point we have a series de data-samples, which each of them is based in time series. However, we are not interested in a time series analysis, therefore it would be needed to compress each time-series based data-sample in an atemporal data-sample.

>>>>

\author[a]{Peter Burggräf}
\author[a]{Johannes Wagner}
\author[a]{Benjamin Koke}
\author[a]{Fabian Steinberg} 
\author[a]{Alejandro R. Pérez M.*}
\author[a]{Lennart Schmallenbach}
\author[b,c]{Jochen Garcke}
\author[b]{Daniela Steffes-lai}
\author[b,d]{Moritz Wolter}

@@

\begin{itemize}
       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
\end{itemize}

@@

Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle. For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so. At this point we have a series de data-samples, which each of them is based in time series. However, we are not interested in a time series analysis, therefore it would be needed to compress each time-series based data-sample in an atemporal data-sample.
